---
title: "Histopathology Research Template"
description: |
  Codes Used in Histopathology Research  
  Data Report for Histopathology Research  
  Example Using Random Generated Fakedata
author: 
  - name: Serdar Balci, MD, Pathologist
    url: https://sbalci.github.io/histopathology-template/
    affiliation: serdarbalci.com
    affiliation_url: https://www.serdarbalci.com/
date: "`r Sys.Date()`"
mail: drserdarbalci@gmail.com
linkedin: "serdar-balci-md-pathologist"
twitter: "serdarbalci"
github: "sbalci"
home: "https://www.serdarbalci.com/"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{xcolor}
- \usepackage{afterpage}
output:
  rmarkdown::html_vignette: 
    css: 
    - !expr system.file("rmarkdown/templates/html_vignette/resources/vignette.css", package = "rmarkdown")
  prettydoc::html_pretty:
    theme: leonids
    highlight: vignette
    toc: true
    number_sections: yes
    css: css/style.css
    includes:
      after_body: _footer.html
  epuRate::epurate:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
  distill::distill_article:
    toc: true
  redoc::redoc:
    highlight_outputs: TRUE
    margins: 1 
    line_numbers: FALSE 
  pdf_document: 
    fig_caption: yes
    highlight: kate
    number_sections: yes
    toc: yes
    latex_engine: lualatex
    toc_depth: 5
    keep_tex: yes
vignette: >
  %\VignetteIndexEntry{Histopathology Research Template}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
bibliography: bib/template.bib
---


---


[Histopathology Research Template 🔬](https://sbalci.github.io/histopathology-template/)


---



# Introduction

- **State the marker of interest, the study objectives, and hypotheses [@Knijn2015]**.^[From Table 1: Proposed items for reporting histopathology studies. Recommendations for reporting histopathology studies: a proposal Virchows Arch (2015) 466:611–615 DOI 10.1007/s00428-015-1762-3]

 


# Materials & Methods

**Describe Materials and Methods as highlighted in [@Knijn2015]**.^[From Table 1: Proposed items for reporting histopathology studies. Recommendations for reporting histopathology studies: a proposal Virchows Arch (2015) 466:611–615 DOI 10.1007/s00428-015-1762-3]

- Describe patient characteristics, and inclusion and exclusion criteria

- Describe treatment details

- Describe the type of material used

- Specify how expression of the biomarker was assessed

- Describe the number of independent (blinded) scorers and how they scored

- State the method of case selection, study design, origin of the cases, and time frame

- Describe the end of the follow-up period and median follow-up time

- Define all clinical endpoints examined

- Specify all applied statistical methods

- Describe how interactions with other clinical/pathological factors were analyzed

---

## Header Codes


```{r header, child = here::here('childRmd', '_header.Rmd')}
```


---


## Generate Fake Data


```{r generate fake data, child = here::here('childRmd', '_generateFakeData.Rmd')}
```


---


## Import Data


```{r importData, child = here::here('childRmd', '_importData.Rmd')}
```


---

## Study Population


```{r brief summary, child = here::here('childRmd', '_briefSummary.Rmd')}
```


<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

**Always Respect Patient Privacy**  
- Health Information Privacy^[https://www.hhs.gov/hipaa/index.html]  
- Kişisel Verilerin Korunması^[[Kişisel verilerin kaydedilmesi ve kişisel verileri hukuka aykırı olarak verme veya ele geçirme Türk Ceza Kanunu'nun 135. ve 136. maddesi kapsamında bizim hukuk sistemimizde suç olarak tanımlanmıştır. Kişisel verilerin kaydedilmesi suçunun cezası 1 ila 3 yıl hapis cezasıdır. Suçun nitelikli hali ise, kamu görevlisi tarafından görevin verdiği yetkinin kötüye kullanılarak veya belirli bir meslek veya sanatın sağladığı kolaylıktan yararlanılarak işlenmesidir ki bu durumda suçun cezası 1.5 ile 4.5 yıl hapis cezası olacaktır.](https://barandogan.av.tr/blog/ceza-hukuku/kisisel-verilerin-ele-gecirilmesi-yayilmasi-baskasina-verilmesi-sucu.html)]  

</div>


\noindent\colorbox{yellow}{
\parbox{\dimexpr\linewidth-2\fboxsep}{

**Always Respect Patient Privacy**  
- Health Information Privacy^[https://www.hhs.gov/hipaa/index.html]  
- Kişisel Verilerin Korunması^[[Kişisel verilerin kaydedilmesi ve kişisel verileri hukuka aykırı olarak verme veya ele geçirme Türk Ceza Kanunu'nun 135. ve 136. maddesi kapsamında bizim hukuk sistemimizde suç olarak tanımlanmıştır. Kişisel verilerin kaydedilmesi suçunun cezası 1 ila 3 yıl hapis cezasıdır. Suçun nitelikli hali ise, kamu görevlisi tarafından görevin verdiği yetkinin kötüye kullanılarak veya belirli bir meslek veya sanatın sağladığı kolaylıktan yararlanılarak işlenmesidir ki bu durumda suçun cezası 1.5 ile 4.5 yıl hapis cezası olacaktır.](https://barandogan.av.tr/blog/ceza-hukuku/kisisel-verilerin-ele-gecirilmesi-yayilmasi-baskasina-verilmesi-sucu.html)]  

}
}



---


## Define Variable Types


```{r variable types, child = here::here('childRmd', '_variableTypes.Rmd')}
```



---


## Overview the Data


```{r overview, child = here::here('childRmd', '_overView.Rmd')}
```




---

# Statistical Analysis

**Learn these tests as highlighted in [@Schmidt2017].**^[Statistical Literacy Among Academic Pathologists: A Survey Study to Gauge Knowledge of Frequently Used Statistical Tests Among Trainees and Faculty. Archives of Pathology & Laboratory Medicine: February 2017, Vol. 141, No. 2, pp. 279-287. https://doi.org/10.5858/arpa.2016-0200-OA]

# Results

**Write results as described in [@Knijn2015]**^[From Table 1: Proposed items for reporting histopathology studies. Recommendations for reporting histopathology studies: a proposal Virchows Arch (2015) 466:611–615 DOI 10.1007/s00428-015-1762-3]

- Describe the number of patients included in the analysis and reason for dropout

- Report patient/disease characteristics (including the biomarker of interest) with the number of missing values

- Describe the interaction of the biomarker of interest with established prognostic variables

- Include at least 90 % of initial cases included in univariate and multivariate analyses

- Report the estimated effect (relative risk/odds ratio, confidence interval, and p value) in univariate analysis

- Report the estimated effect (hazard rate/odds ratio, confidence interval, and p value) in multivariate analysis

- Report the estimated effects (hazard ratio/odds ratio, confidence interval, and p value) of other prognostic factors included in multivariate analysis



---


<!-- ## Data Dictionary -->

<!-- ```{r data dictionary, child = here::here('childRmd', '_dataDictionary.Rmd')} -->
<!-- ``` -->

<!-- --- -->


<!-- ## Clean and Recode Data -->

<!-- ```{r clean and recode, child = here::here('childRmd', '_cleanRecode.Rmd')} -->
<!-- ``` -->

<!-- --- -->

<!-- ## Impute Missing Data -->

<!-- ```{r impute, child = here::here('childRmd', '_impute.Rmd')} -->
<!-- ``` -->

<!-- --- -->

<!-- \pagebreak -->


## Descriptive Statistics


```{r descriptives, child = here::here('childRmd', '_descriptives.Rmd')}
```


---

<!-- \newpage -->
<!-- \blandscape -->

<!-- ```{r crossTables, child = here::here('childRmd', '_crossTables.Rmd')} -->
<!-- ``` -->

<!-- \elandscape -->


<!-- ```{r plots, child = here::here('childRmd', '_plots.Rmd')} -->
<!-- ``` -->




<!-- ```{r pairedTests, child = here::here('childRmd', '_pairedTests.Rmd')} -->
<!-- ``` -->



<!-- ```{r hypothesisTests, child = here::here('childRmd', '_hypothesisTests.Rmd')} -->
<!-- ``` -->

<!-- \newpage -->
<!-- \blandscape -->



<!-- ```{r ROC, child = here::here('childRmd', '_ROC.Rmd')} -->
<!-- ``` -->


<!-- ```{r Decision Tree, child = here::here('childRmd', '_decisionTree.Rmd')} -->
<!-- ``` -->



## Survival Analysis


```{r survival, child = here::here('childRmd', '_survival.Rmd')}
```


---

<!-- # Interactive Survival Analysis -->

<!-- ```{r shiny survival, child = here::here('childRmd', '_shinySurvival.Rmd')} -->
<!-- ``` -->


<!-- --- -->

<!-- \elandscape -->


<!-- # Models -->


<!-- ```{r models, child = here::here('childRmd', '_models.Rmd')} -->
<!-- ``` -->


<!-- --- -->

<!-- \pagebreak -->



<!-- ```{r comments, child = here::here('childRmd', '_comments.Rmd')} -->
<!-- ``` -->

---

\pagebreak


# Discussion

- Interpret the results in context of the working hypothesis elaborated in the introduction and other relevant studies; include a discussion of limitations of the study.

- Discuss potential clinical applications and implications for future research

\pagebreak


# Footer

```{r footer, child = here::here('childRmd', '_footer.Rmd')}
```

<!-- --- -->

<!-- \pagebreak -->


<!-- **push all changes to GitHub repository**  -->

<!-- ```{r git update} -->
<!-- source(file = here::here("R", "force_git.R")) -->
<!-- ``` -->


<!-- --- -->


# References


