**Codes for defining variable types**.^[See [`childRmd/_06variableTypes.Rmd`](https://github.com/sbalci/histopathology-template/blob/master/childRmd/_06variableTypes.Rmd) file for other codes]




**print column names as vector**


```{r print names as vector}
dput(names(mydata))
```

### Find Key Columns

#### Find ID and key columns to exclude from analysis

```
vctrs::vec_assert()

dplyr::all_equal()

arsenal::compare()

visdat::vis_compare()

```

See the code as function in [`R/find_key.R`](https://github.com/sbalci/histopathology-template/blob/master/R/find_key.R). 


```{r find ID and key columns}
keycolumns <-  
    mydata %>%  
    sapply(., FUN = dataMaid::isKey) %>%  
    tibble::as_tibble() %>%  
    dplyr::select(  
        which(.[1, ] == TRUE)  
    ) %>%   
    names()  
keycolumns  
```


### Variable Types

**Get variable types**

```{r get variable types inspectdf}
mydata %>% 
  dplyr::select(-keycolumns) %>% 
inspectdf::inspect_types()
```



```{r describer 1}
mydata %>% 
    dplyr::select(-keycolumns,
           -contains("Date")) %>% 
  describer::describe() %>% 
  knitr::kable(format = "markdown")
```


**Plot variable types**

```{r variable type plot inspectdf}
mydata %>% 
    dplyr::select(-keycolumns) %>% 
  inspectdf::inspect_types() %>% 
  inspectdf::show_plot()
```



```{r variable type plot visdat}
# https://github.com/ropensci/visdat
# http://visdat.njtierney.com/articles/using_visdat.html
# https://cran.r-project.org/web/packages/visdat/index.html
# http://visdat.njtierney.com/

# visdat::vis_guess(mydata)

visdat::vis_dat(mydata)
```


```{r variable type plot explore}
mydata %>% explore::explore_tbl()
```



### Define Variable Types


#### Find `character` variables

```{r find character variables inspectdf}
mydata %>% 
    dplyr::select(-keycolumns) %>% 
    inspectdf::inspect_types() %>% 
    dplyr::filter(type == "character") %>% 
    dplyr::select(col_name) %>% 
    dplyr::pull() %>% 
    unlist() -> characterVariables

characterVariables
```


#### Find `categorical` variables

```{r find categorical variables}
mydata %>%
    dplyr::select(-keycolumns,
                  -contains("Date")
                  ) %>%
  describer::describe() %>% 
    janitor::clean_names() %>% 
    dplyr::filter(column_type == "factor") %>% 
    dplyr::select(column_name) %>% 
    dplyr::pull() -> categoricalVariables

categoricalVariables
```



#### Find `continious` variables


```{r find continious variables describer}
mydata %>%
    dplyr::select(-keycolumns,
                  -contains("Date")) %>%
  describer::describe() %>% 
    janitor::clean_names() %>% 
    dplyr::filter(column_type == "numeric" | column_type == "double") %>% 
    dplyr::select(column_name) %>% 
    dplyr::pull() -> continiousVariables

continiousVariables
```


#### Find `numeric` variables



```{r find numeric variables inspectdf}
mydata %>% 
    dplyr::select(-keycolumns) %>% 
inspectdf::inspect_types() %>% 
  dplyr::filter(type == "numeric") %>% 
  dplyr::select(col_name) %>% 
  dplyr::pull() %>% 
  unlist() -> numericVariables

numericVariables
```


#### Find `integer` variables


```{r find integer variables inspectdf}
mydata %>% 
    dplyr::select(-keycolumns) %>% 
inspectdf::inspect_types() %>% 
  dplyr::filter(type == "integer") %>% 
  dplyr::select(col_name) %>% 
  dplyr::pull() %>% 
  unlist() -> integerVariables

integerVariables
```


#### Find `list` variables

```{r find list variables inspectdf}
mydata %>% 
    dplyr::select(-keycolumns) %>% 
inspectdf::inspect_types() %>% 
  dplyr::filter(type == "list") %>% 
  dplyr::select(col_name) %>% 
  dplyr::pull() %>% 
  unlist() -> listVariables
listVariables
```


#### Find `date` variables

```{r find Date variables}
is_date <- function(x) inherits(x, c("POSIXct", "POSIXt"))

dateVariables <- 
names(which(sapply(mydata, FUN = is_date) == TRUE))
dateVariables
```


