## Plots

**Codes for generating Plots**.^[See [`childRmd/_13plots.Rmd`](https://github.com/sbalci/histopathology-template/blob/master/childRmd/_13plots.Rmd) file for other codes]

## Categorical Variables


```{r define variables, eval=FALSE, include=FALSE, eval=FALSE, include=FALSE}
dependent <- c("dependent1",
               "dependent2"
                 )

explanatory <- c("explanatory1",
                 "explanatory2"
                 )
```




```{r select categorical, eval=FALSE, include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical <- mydata %>% 
    select(-var1,
           -var2
    )
```



```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- explanatory[1]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[2]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```

```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```



```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[3]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```



```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[4]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[5]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[6]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[7]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[8]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[9]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[10]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[11]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[12]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[13]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[14]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```

```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[15]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```


```{r include=FALSE, eval=FALSE, include=FALSE}
mydataCategorical_variable <- NA
dependent2 <- NA
mydataCategorical_variable <- explanatory[16]
dependent2 <- dependent[!dependent %in% mydataCategorical_variable]
source(here::here("R", "gc_plot_cat.R"))
```


```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd'), eval=FALSE, include=FALSE}
```



```{r SmartEDA column chart, eval=FALSE, include=FALSE}
## column chart
SmartEDA::ExpCatViz(
  Carseats,
  target = "Urban",
  fname = NULL,
  clim = 10,
  col = NULL,
  margin = 2,
  Page = c(2, 1),
  sample = 2
)
```


```{r SmartEDA bar graph, eval=FALSE, include=FALSE}
## Stacked bar graph
SmartEDA::ExpCatViz(
  Carseats,
  target = "Urban",
  fname = NULL,
  clim = 10,
  col = NULL,
  margin = 2,
  Page = c(2, 1),
  sample = 2
)
```


```{r SmartEDA information values, eval=FALSE, include=FALSE}
## Variable importance graph using information values
SmartEDA::ExpCatStat(
  Carseats,
  Target = "Urban",
  result = "Stat",
  Pclass = "Yes",
  plot = TRUE,
  top = 20,
  Round = 2
)
```




```{r inspectdf plot, eval=FALSE, include=FALSE}
inspectdf::inspect_cat(starwars) %>% inspectdf::show_plot()
```



```{r inspectdf plot 2, eval=FALSE, include=FALSE}
inspectdf::inspect_cat(starwars) %>% 
  inspectdf::show_plot(high_cardinality = 1)
```



```{r inspectdf categorical plot, eval=FALSE, include=FALSE}
inspectdf::inspect_cat(star_1, star_2) %>% inspectdf::show_plot()
```






<!-- ## Continious Variables -->


<!-- ```{r} -->
<!-- mydataContinious <- mydata %>%  -->
<!--     select( -->
<!--         Yas, -->
<!--         TumorCapi -->
<!--     ) -->
<!-- ``` -->



<!-- ```{r include=FALSE} -->
<!-- source(here::here("R", "gc_plot_cont.R")) -->
<!-- ``` -->



<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeContiniousPlots.Rmd')} -->
<!-- ``` -->


### Plots

<!-- ## Categorical Variables -->


<!-- ```{r} -->
<!-- dependent <- c("Lauren", -->
<!--                "CD44", -->
<!--                "Her2", -->
<!--                "MMR2", -->
<!--                  "TumorPDL1gr1", -->
<!--                  "TumorPDL1gr5", -->
<!--                  "inflPDL1gr1", -->
<!--                  "inflPDL1gr5" -->
<!--                  ) -->

<!-- explanatory <- c("Cinsiyet", -->
<!--                  # "TumorYerlesimi", -->
<!--                  "Lauren", -->
<!--                  "Grade", -->
<!--                  "T_stage", -->
<!--                  "N_stage", -->
<!--                  "M_stage", -->
<!--                  "CD44", -->
<!--                  "Her2", -->
<!--                  "MMR2", -->
<!--                  "TumorPDL1gr1", -->
<!--                  "TumorPDL1gr5", -->
<!--                  "inflPDL1gr1", -->
<!--                  "inflPDL1gr5", -->
<!--                  "LVI", -->
<!--                  "PNI", -->
<!--                  "LenfNoduMetastazi") -->
<!-- ``` -->




<!-- ```{r} -->
<!-- mydataCategorical <- mydata %>%  -->
<!--     select(-Yas, -->
<!--            -TumorCapi, -->
<!--            -CerrahiTarih, -->
<!--            -genel_sagkalim, -->
<!--            -SonTarih, -->
<!--            -TNM -->
<!--     ) -->
<!-- ``` -->



<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- explanatory[1] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[2] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->

<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->



<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[3] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->



<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[4] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[5] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[6] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[7] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[8] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[9] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[10] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[11] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[12] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[13] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[14] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->

<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[15] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- mydataCategorical_variable <- NA -->
<!-- dependent2 <- NA -->
<!-- mydataCategorical_variable <- explanatory[16] -->
<!-- dependent2 <- dependent[!dependent %in% mydataCategorical_variable] -->
<!-- source(here::here("R", "gc_plot_cat.R")) -->
<!-- ``` -->


<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeCategoricalPlots.Rmd')} -->
<!-- ``` -->




## Continious Variables


```{r, eval=FALSE, include=FALSE}
# mydataContinious
```



<!-- ```{r include=FALSE} -->
<!-- source(here::here("R", "gc_plot_cont.R")) -->
<!-- ``` -->



<!-- ```{r generatedCode, child = here::here('childRmd', 'generatedCodeContiniousPlots.Rmd')} -->
<!-- ``` -->


<!-- ```{r} -->
<!-- mydata %>%  -->
<!--     select(starts_with("Slide")) %>%  -->
<!--     pivot_longer(cols = everything()) %>%  -->
<!-- ggstatsplot::ggwithinstats(data = ., x = name, y = value) -->
<!-- ``` -->



```{r eval=FALSE, eval=FALSE, include=FALSE}
mydata %>%
    select(institution, starts_with("Slide")) %>%
    pivot_longer(cols = starts_with("Slide")) %>%
    ggplot(., aes(name, value)) -> p
p + geom_jitter() 
p + geom_jitter(aes(colour = institution)) 
```


```{r eval=FALSE, eval=FALSE, include=FALSE}
dxchanges <- mydata %>%
    select(bx_no, starts_with("Slide")) %>% 
    filter(complete.cases(.)) %>%
    group_by(Slide1_infiltrative, Slide2_Medium, Slide3_Demarcated) %>% 
    tally()

library(ggalluvial)

ggplot(data = dxchanges,
       aes(axis1 = Slide1_infiltrative, axis2 = Slide2_Medium, axis3 = Slide3_Demarcated,
           y = n)) +
  scale_x_discrete(limits = c("Slide1", "Slide2", "Slide3"),
                   expand = c(.1, .05)
                   ) +
  xlab("Slide") +
  geom_alluvium(aes(fill = Slide1_infiltrative,
                    colour = Slide1_infiltrative
                    )) +
  geom_stratum() +
  geom_text(stat = "stratum", label.strata = TRUE) +
  theme_minimal() +
  ggtitle("PanNET")

```





<!-- ```{r webgl=TRUE, results='hide'} -->
<!-- # library -->
<!-- library(rgl) -->

<!-- # This is to output a rgl plot in a rmarkdown document. Note that you must add webgl=TRUE, results='hide' in the chunck header -->
<!-- library(knitr) -->
<!-- knit_hooks$set(webgl = hook_webgl) -->

<!-- # Data: the iris data is provided by R -->
<!-- # data <- iris -->

<!-- # Add a new column with color -->
<!-- # mycolors <- c('royalblue1', 'darkcyan', 'oldlace', 'red', 'orange') -->
<!-- # data$color <- mycolors[ as.numeric(dxchanges$Slide1_infiltrative) ] -->

<!-- # Plot -->
<!-- par(mar=c(0,0,0,0)) -->
<!-- plot3d(  -->
<!--   x=dxchanges$Slide1_infiltrative, y=dxchanges$Slide2_Medium, z=dxchanges$Slide3_Demarcated,  -->
<!--   col = dxchanges$Slide1_infiltrative, -->
<!--   type = 's',  -->
<!--   radius = .1, -->
<!--   xlab="Slide1_infiltrative", ylab="Sepal Width", zlab="Petal Length") -->

<!-- writeWebGL(filename = here::here("HtmlWidget/3dscatter2.html") ,  width=600, height=600) -->

<!-- ``` -->




<!-- ```{r} -->
<!-- library(ggparallel) -->
<!-- ggparallel(vars = list("Slide1_infiltrative", "Slide2_Medium", "Slide3_Demarcated"),  -->
<!--            data = dxchanges) -->

<!-- ``` -->


```{r SmartEDA Boxplot by category, eval=FALSE, include=FALSE}
## Generate Boxplot by category
SmartEDA::ExpNumViz(
  mtcars,
  target = "gear",
  type = 2,
  nlim = 25,
  fname = file.path(here::here(), "Mtcars2"),
  Page = c(2, 2)
)
```


```{r SmartEDA density plot by category, eval=FALSE, include=FALSE}
## Generate Density plot
SmartEDA::ExpNumViz(
  mtcars,
  target = NULL,
  type = 3,
  nlim = 25,
  fname = file.path(here::here(), "Mtcars3"),
  Page = c(2, 2)
)
```


```{r SmartEDA scatterplot by category, eval=FALSE, include=FALSE}
## Generate Scatter plot
SmartEDA::ExpNumViz(
  mtcars,
  target = "carb",
  type = 3,
  nlim = 25,
  fname = file.path(here::here(), "Mtcars4"),
  Page = c(2, 2)
)
```


```{r SmartEDA scatterplots by category 2, eval=FALSE, include=FALSE}
SmartEDA::ExpNumViz(mtcars, target = "am", scatter = TRUE)
```



### Interactive graphics {#interactive}

***

R allows to build any type of [interactive graphic](https://www.r-graph-gallery.com/interactive-charts/). My favourite library is [plotly](https://www.r-graph-gallery.com/get-the-best-from-ggplotly/) that will turn any of your ggplot2 graphic interactive in one supplementary line of code. Try to hover points, to select a zone, to click on the legend.
<br><br>

```{r, message=FALSE, warning=FALSE, eval=FALSE, echo=TRUE, fig.align="center"}
library(ggplot2)
library(plotly)
library(gapminder)
 
p <- gapminder %>%
  filter(year==1977) %>%
  ggplot( aes(gdpPercap, lifeExp, size = pop, color=continent)) +
  geom_point() +
  scale_x_log10() +
  theme_bw()
 
ggplotly(p)
```



---

```{r}
scales::show_col(colours(), cex_label = .35)
```


```{r gistr}
gistr::gist("https://gist.github.com/sbalci/834ebc154c0ffcb7d5899c42dd3ab75e") %>% 
  gistr::embed() -> embedgist
```


`r embedgist`


<script src="https://gist.github.com/sbalci/834ebc154c0ffcb7d5899c42dd3ab75e.js"></script>



---

### Alluvial

```{r}

# https://stackoverflow.com/questions/43053375/weighted-sankey-alluvial-diagram-for-visualizing-discrete-and-continuous-panel/48133004

library(tidyr)
library(dplyr)
library(alluvial)
library(ggplot2)
library(forcats)

set.seed(42)
individual <- rep(LETTERS[1:10],each=2)
timeperiod <- paste0("time_",rep(1:2,10))
discretechoice <- factor(paste0("choice_",sample(letters[1:3],20, replace=T)))
continuouschoice <- ceiling(runif(20, 0, 100))
d <- data.frame(individual, timeperiod, discretechoice, continuouschoice)

```

```{r}
# stacked bar diagram of discrete choice by individual
g <- ggplot(data=d,aes(timeperiod,fill=fct_rev(discretechoice)))
g + geom_bar(position="stack") + guides(fill=guide_legend(title=NULL))
```


```{r}
# alluvial diagram of discrete choice by individual
d_alluvial <- d %>%
  select(individual,timeperiod,discretechoice) %>%
  spread(timeperiod,discretechoice) %>%
  group_by(time_1,time_2) %>%
  summarize(count=n()) %>%
  ungroup()
alluvial(select(d_alluvial,-count),freq=d_alluvial$count)
```


```{r}
# stacked bar diagram of discrete choice, weighting by continuous choice
g + geom_bar(position="stack",aes(weight=continuouschoice))
```


```{r}
library(ggalluvial)
ggplot(
  data = d,
  aes(
    x = timeperiod,
    stratum = discretechoice,
    alluvium = individual,
    y = continuouschoice
  )
) +
  geom_stratum(aes(fill = discretechoice)) +
  geom_flow()
```






```{r eval=FALSE, include=FALSE}
 # use of strata and labels
ggplot(as.data.frame(Titanic),
       aes(y = Freq,axis1 = Class, axis2 = Sex, axis3 = Age)) +
  geom_flow() +
  scale_x_discrete(limits = c("Class", "Sex", "Age")) +
  geom_stratum() + 
  geom_text(stat = "stratum", infer.label = TRUE) +
  ggtitle("Alluvial plot of Titanic passenger demographic data")

# use of facets
ggplot(as.data.frame(Titanic),aes(y = Freq,axis1 = Class, axis2 = Sex)) +geom_flow(aes(fill = Age), width = .4) +geom_stratum(width = .4) +geom_text(stat = "stratum", infer.label = TRUE, size = 3) +scale_x_discrete(limits = c("Class", "Sex")) +facet_wrap(~ Survived, scales = "fixed")
# time series alluvia of WorldPhones 
wph <- as.data.frame(as.table(WorldPhones))
names(wph) <- c("Year", "Region", "Telephones")
ggplot(wph,aes(x = Year, alluvium = Region, y = Telephones)) +geom_flow(aes(fill = Region, colour = Region), width = 0)
# rightward flow aesthetics for vaccine survey datad
data(vaccinations)
levels(vaccinations$response) <- rev(levels(vaccinations$response))

ggplot(vaccinations,
       aes(x = survey, 
           stratum = response, 
           alluvium = subject,
           y = freq, 
           fill = response 
           label = round(a, 3)
           )
       ) +
  geom_lode() + 
  geom_flow() +
  geom_stratum(alpha = 0) +
  geom_text(stat = "stratum")

```


  
```{r}
CD44changes <- mydata %>%
    dplyr::select(TumorCD44, TomurcukCD44, PeritumoralTomurcukGr4) %>% 
    dplyr::filter(complete.cases(.)) %>%
    dplyr::group_by(TumorCD44, TomurcukCD44, PeritumoralTomurcukGr4) %>% 
    dplyr::tally()

library(ggalluvial)

ggplot(data = CD44changes,
       aes(axis1 = TumorCD44, axis2 = TomurcukCD44,
           y = n)) +
  scale_x_discrete(limits = c("TumorCD44", "TomurcukCD44"),
                   expand = c(.1, .05)
                   ) +
  xlab("Tumor Tomurcuk") +
  geom_alluvium(aes(fill = PeritumoralTomurcukGr4,
                    colour = PeritumoralTomurcukGr4                    )) +
  geom_stratum(alpha = .5) +
  geom_text(stat = "stratum", infer.label = TRUE) +
  # geom_text(stat = 'alluvium', infer.label = TRUE) +
  theme_minimal() +
  ggtitle("Changes in CD44")
```

  



