**Codes for explaining the software and the packages that are used in the analysis**^[See [`childRmd/_23footer.Rmd`](https://github.com/sbalci/histopathology-template/blob/master/childRmd/_23footer.Rmd) file for other codes]


### Save Final Data  {.appendix}  

```{r save final data}
projectName <- list.files(path = here::here(), pattern = "Rproj")
projectName <- gsub(pattern = ".Rproj", replacement = "", x = projectName)

analysisDate <- as.character(Sys.Date())

imageName <- paste0(projectName, analysisDate, ".RData")

save.image(file = here::here("data", imageName))

rdsName <- paste0(projectName, analysisDate, ".rds")

readr::write_rds(x = mydata, path = here::here("data", rdsName))

saveRDS(object = mydata, file = here::here("data", rdsName))

excelName <- paste0(projectName, analysisDate, ".xlsx")

rio::export(
  x = mydata,
  file = here::here("data", excelName),
  format = "xlsx"
)

# writexl::write_xlsx(mydata, here::here("data", excelName))

print(glue::glue(
    "saved data after analysis to ",
    rownames(file.info(here::here("data", excelName))),
    " : ",
    as.character(
        file.info(here::here("data", excelName))$ctime
    )
    )
)
```


```{r save final data 2, eval=FALSE, include=FALSE}
# pacman::p_load(here, lubridate, glue)
# here::here("data", glue("{today()}_trends.csv"))
```



---


\pagebreak


### Final Data Summary {.appendix}  


```r
# use summarytools to generate final data summary
# summarytools::view(summarytools::dfSummary(x = mydata
#                                            , style = "markdown"))
```


```{r summarytools final summary, eval=FALSE, error=FALSE, warning=FALSE, include=FALSE}
# mydata %>% select(
#     -c(
#         rapor_yil,
#         rapor_no,
#         protokol_no,
#         istek_tarihi,
#         nux_yada_met_varsa_tarihi,
#         son_hastane_vizit_tarihi,
#         Outcome
#     )
# ) -> finalSummary
# 
# summarytools::view(summarytools::dfSummary(x = finalSummary
#                                            , style = "markdown"))
```


---

\pagebreak



### Software and Libraries Used {.appendix}  

Why and how to cite software and packages?^[Smith AM, Katz DS, Niemeyer KE, FORCE11 Software Citation Working Group. (2016) Software Citation Principles. PeerJ Computer Science 2:e86. DOI: 10.7717/peerj-cs.86 https://www.force11.org/software-citation-principles]


```{r citation}
citation()
```


The jamovi project (2019). jamovi. (Version 0.9) [Computer Software]. Retrieved from https://www.jamovi.org.  
R Core Team (2018). R: A Language and envionment for statistical computing. [Computer software]. Retrieved from https://cran.r-project.org/.  
Fox, J., & Weisberg, S. (2018). car: Companion to Applied Regression. [R package]. Retrieved from https://cran.r-project.org/package=car.
Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
Data processing was carried out with R (R Core Team, 2019) and the easystats ecosystem (Lüdecke, Waggoner, & Makowski, 2019; Makowski, Ben-Shachar, & Lüdecke, 2019)



```{r library citation as report, results='asis'}
report::cite_packages(session = sessionInfo())
```


```{r show library citation as report, echo=TRUE, eval=FALSE, results='asis'}
report::show_packages(session = sessionInfo()) %>% 
    kableExtra::kable()
```


```{r library citations}
citation("tidyverse")
citation("readxl")
citation("janitor")
# citation("report")
citation("finalfit")
# citation("ggstatsplot")
```


```{r write libraries as bib file}
if(!dir.exists(here::here("bib"))) {dir.create(here::here("bib"))}

knitr::write_bib(x = c(.packages(), "knitr", "shiny"),
                 file = here::here("bib", "packages.bib")
)
```


---

\pagebreak

### Session Info {.appendix} 

```{r session info}
sessionInfo()
```

\pagebreak

---

### Loaded packages {.appendix} 

```{r session info by pacman, echo=TRUE, eval=FALSE}
pacman::p_loaded(all = TRUE)
```


---

\pagebreak



### Notes {.appendix}  

Last update on `r as.character(Sys.time())`  

Serdar Balci, MD, Pathologist  
drserdarbalci@gmail.com  
https://rpubs.com/sbalci/CV   

---

\pagebreak

## Code Appendix

**Use following chunk options to include all codes below the report.**

```r
{r, echo=TRUE, eval=FALSE, ref.label=knitr::all_labels()}
```



```{r, echo=TRUE, eval=FALSE, ref.label=knitr::all_labels()}
```

