**Codes for explaining the software and the packages that are used in the analysis**^[See [`childRmd/_23footer.Rmd`](https://github.com/sbalci/histopathology-template/blob/master/childRmd/_23footer.Rmd) file for other codes]


### Save Final Data  {.appendix}  

```{r save final data, cache=FALSE}
projectName <- list.files(path = here::here(), pattern = "Rproj")
projectName <- gsub(pattern = ".Rproj", replacement = "", x = projectName)

analysisDate <- as.character(Sys.Date())

imageName <- paste0(projectName, analysisDate, ".RData")

save.image(file = here::here("data", imageName))

rdsName <- paste0(projectName, analysisDate, ".rds")

readr::write_rds(x = mydata, path = here::here("data", rdsName))

saveRDS(object = mydata, file = here::here("data", rdsName))

excelName <- paste0(projectName, analysisDate, ".xlsx")

rio::export(
  x = mydata,
  file = here::here("data", excelName),
  format = "xlsx"
)

excelName2 <- paste0(projectName, "-2-", analysisDate, ".xlsx")

si <- sessioninfo::session_info()
writexl::write_xlsx(x = 
  list(
    maindata = mydata,
    meta_platform = (as.data.frame(unclass(si$platform))),
    meta_packages = si$packages
  ),
  path = here::here("data", excelName2)
)








# writexl::write_xlsx(mydata, here::here("data", excelName))

print(glue::glue(
    "saved data after analysis to ",
    rownames(file.info(here::here("data", excelName))),
    " : ",
    as.character(
        file.info(here::here("data", excelName))$ctime
    )
    )
)
```


```{r download button, cache=FALSE}
mydata %>% 
  downloadthis::download_this(
    output_name = excelName,
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "default"
  )

mydata %>% 
  downloadthis::download_this(
    output_name = excelName,
    output_extension = ".xlsx",
    button_label = "Download data as xlsx",
    button_type = "primary"
  )
```




```{r save final data 2, eval=FALSE, include=FALSE, cache=FALSE}
# pacman::p_load(here, lubridate, glue)
# here::here("data", glue("{today()}_trends.csv"))
```



---


\pagebreak


### Final Data Summary {.appendix}  


```r
# use summarytools to generate final data summary
# summarytools::view(summarytools::dfSummary(x = mydata
#                                            , style = "markdown"))
```


```{r summarytools final summary, eval=FALSE, error=FALSE, warning=FALSE, include=FALSE, cache=FALSE}
# mydata %>% select(
#     -c(
#         rapor_yil,
#         rapor_no,
#         protokol_no,
#         istek_tarihi,
#         nux_yada_met_varsa_tarihi,
#         son_hastane_vizit_tarihi,
#         Outcome
#     )
# ) -> finalSummary
# 
# summarytools::view(summarytools::dfSummary(x = finalSummary
#                                            , style = "markdown"))
```


---

\pagebreak



### Software and Libraries Used {.appendix}  

Why and how to cite software and packages?^[Smith AM, Katz DS, Niemeyer KE, FORCE11 Software Citation Working Group. (2016) Software Citation Principles. PeerJ Computer Science 2:e86. DOI: 10.7717/peerj-cs.86 https://www.force11.org/software-citation-principles]


```{r citation, cache=FALSE}
citation()
```


The jamovi project (2019). jamovi. (Version 0.9) [Computer Software]. Retrieved from https://www.jamovi.org.  
R Core Team (2018). R: A Language and envionment for statistical computing. [Computer software]. Retrieved from https://cran.r-project.org/.  
Fox, J., & Weisberg, S. (2018). car: Companion to Applied Regression. [R package]. Retrieved from https://cran.r-project.org/package=car.
Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
Data processing was carried out with R (R Core Team, 2019) and the easystats ecosystem (Lüdecke, Waggoner, & Makowski, 2019; Makowski, Ben-Shachar, & Lüdecke, 2019)



```{r library citation as report, results='asis', cache=FALSE}
report::cite_packages(session = sessionInfo())
```


```{r show library citation as report, echo=TRUE, eval=FALSE, results='asis', cache=FALSE}
report::show_packages(session = sessionInfo()) %>% 
    kableExtra::kable()
```


```{r library citations, cache=FALSE}
# citation("tidyverse")
citation("readxl")
citation("janitor")
# citation("report")
citation("finalfit")
# citation("ggstatsplot")
```


```{r write libraries as bib file, cache=FALSE}
if(!dir.exists(here::here("bib"))) {dir.create(here::here("bib"))}

knitr::write_bib(x = c(.packages(), "knitr", "shiny"),
                 file = here::here("bib", "packages.bib")
)
```


---

\pagebreak

### Session Info {.appendix} 

```{r session info, cache=FALSE}
sessionInfo()
```



```{r session info 2, cache=FALSE}
sessioninfo::os_name()

sessioninfo::package_info()

sessioninfo::platform_info()

sessioninfo::session_info()

```



\pagebreak

---

### Loaded packages {.appendix} 

```{r session info by pacman, echo=TRUE, eval=FALSE, cache=FALSE}
pacman::p_loaded(all = TRUE)
```


```{r eval=FALSE, include=FALSE, cache=FALSE}
search()
```

```{r eval=FALSE, include=FALSE, cache=FALSE}
library()
```


```{r eval=FALSE, include=FALSE, cache=FALSE}
installed.packages()[1:5, c("Package", "Version")]
installed.packages()
```


---


### Reproducibility


<details><summary>Reproducibility receipt</summary>


```{r, cache=FALSE}
# https://twitter.com/MilesMcBain/status/1263272935197782016

## datetime
Sys.time()

## repository
git2r::repository()

## sessionInfo
sessionInfo()

```



</details>



---

\pagebreak



### Notes {.appendix}  

Last update on $ `r as.character(Sys.time())` $  

[Serdar Balci, MD, Pathologist](https://www.serdarbalci.com/)  
serdarbalci@serdarbalci.com  
https://rpubs.com/sbalci/CV   
https://github.com/sbalci  
https://sbalci.github.io/  
[Patoloji Notları](http://www.patolojinotlari.com/)  
[ParaPathology](http://www.parapathology.com/)  
https://twitter.com/serdarbalci  


---

\pagebreak

## Code Appendix

**Use following chunk options to include all codes below the report.**

```r
{r, echo=TRUE, eval=FALSE, ref.label=knitr::all_labels()}
```



```{r, echo=TRUE, eval=FALSE, ref.label=knitr::all_labels(), cache=FALSE}
```

