**Codes for Descriptive Statistics**^[See [`childRmd/_descriptives.Rmd`](https://github.com/sbalci/histopathology-template/blob/master/childRmd/_descriptives.Rmd) file for other codes]


### Table One   

**Report Data properties via report 📦**

```{r report data}
mydata %>%
  dplyr::select(-dplyr::contains("Date")) %>%
  report::report()
```


**Table 1 via arsenal 📦**

```{r arsenal Table 1, results='asis'}
# cat(names(mydata), sep = " + \n")
library(arsenal)
tab1 <- arsenal::tableby(
  ~ Sex +
    Age +
    Race +
    PreinvasiveComponent +
    LVI +
    PNI +
    Death +
    Group +
    Grade +
    TStage +
    `Anti-X-intensity` +
    `Anti-Y-intensity` +
    LymphNodeMetastasis +
    Valid +
    Smoker +
    Grade_Level
  ,
  data = mydata
)
summary(tab1)
```



**Table 1 via tableone 📦**

<!-- https://cran.r-project.org/web/packages/tableone/index.html -->
<!-- https://cran.r-project.org/web/packages/tableone/vignettes/introduction.html -->
<!-- library(survival) -->
<!-- data(pbc) -->


```{r tableone}
library(tableone)
mydata %>% 
  select(-keycolumns,
         -dateVariables
         ) %>% 
tableone::CreateTableOne(data = .)
```


```{r tableone 2, eval=FALSE, include=FALSE}
# CreateTableOne(vars = myVars, data = mydata, factorVars = characterVariables)
```


```{r tableone 3, eval=FALSE, include=FALSE}
# tab <- CreateTableOne(vars = myVars, data = pbc, factorVars = catVars)
# print(tab, showAllLevels = TRUE)
# ?print.TableOne
# summary(tab)
```




```{r tableone nonnormal values, eval=FALSE, include=FALSE}
# print(tab, nonnormal = biomarkers)
```


```{r tableone copy to excel, eval=FALSE, include=FALSE}
# print(tab, nonnormal = biomarkers, exact = "stage", quote = TRUE, noSpaces = TRUE)
```


```{r tableone export to csv, eval=FALSE, include=FALSE}
# tab3Mat <- print(tab3, nonnormal = biomarkers, exact = "stage", quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
# write.csv(tab3Mat, file = "myTable.csv")
```


<!-- **Table 1 via atable 📦** -->

<!-- https://cran.r-project.org/web/packages/atable/vignettes/atable_usage.pdf -->
<!-- https://journal.r-project.org/archive/2019/RJ-2019-001/index.html -->



**Descriptive Statistics of Continuous Variables**

```{r summarytools descriptives 1}
mydata %>% 
  select(
    continiousVariables,
    numericVariables,
    integerVariables
  ) %>% 
summarytools::descr(., style = 'rmarkdown')
```



```{r summarytools descriptives 2}
print(summarytools::descr(mydata), method = 'render', table.classes = 'st-small')
```
 


```{r summarytools descriptives 3}
mydata %>% 
  summarytools::descr(.,
                      stats = "common",
                      transpose = TRUE,
                      headings = FALSE
                      )
```



```{r summarytools descriptives 4}
mydata %>% 
  summarytools::descr(stats = "common") %>%
  summarytools::tb()
```


```{r summarytools descriptives 5}
mydata$Sex %>% 
  summarytools::freq(cumul = FALSE, report.nas = FALSE) %>%
  summarytools::tb()
```




```{r explore descriptive statistics 1}
mydata %>%
  explore::describe() %>%
  dplyr::filter(unique < 5)
```


```{r explore descriptive statistics 2}
mydata %>%
  explore::describe() %>%
  dplyr::filter(na > 0)
```





```{r describe via explore}
mydata %>% explore::describe()
```



### Categorical Variables

**Use `R/gc_desc_cat.R` to generate `gc_desc_cat.Rmd` containing descriptive statistics for categorical variables**


```{r generate Code descriptive, message=FALSE, warning=FALSE}
source(here::here("R", "gc_desc_cat.R"))
```


```{r generatedCodeDescriptives, child = here::here('childRmd', 'gc_desc_cat.Rmd'), echo=TRUE}
```


```{r tableone categorical, eval=FALSE, include=FALSE}
tab <- 
  mydata %>% 
  select(
    -keycolumns
    ) %>% 
  tableone::CreateTableOne(data = .)
?print.CatTable
tab$CatTable
```



```{r summarytools categorical, echo=TRUE, eval=FALSE}
race_stats <- summarytools::freq(mydata$Race) 
print(race_stats,
      report.nas = FALSE,
      totals = FALSE,
      display.type = FALSE,
      Variable.label = "Race Group"
      )
```




```{r explore categorical variables}
mydata %>% explore::describe(PreinvasiveComponent)
```



```{r SmartEDA 1}
## Frequency or custom tables for categorical variables
SmartEDA::ExpCTable(
  mydata,
  Target = NULL,
  margin = 1,
  clim = 10,
  nlim = 5,
  round = 2,
  bin = NULL,
  per = T
)
```



```{r inspectdf 2}
inspectdf::inspect_cat(mydata)

inspectdf::inspect_cat(mydata)$levels$Group
```



#### Split-Group Stats Categorical


```{r summarytools Split-Group categorical, echo=TRUE, eval=FALSE}
library(summarytools)

grouped_freqs <- stby(data = mydata$Smoker, 
                      INDICES = mydata$Sex, 
                      FUN = freq, cumul = FALSE, report.nas = FALSE)

grouped_freqs %>% tb(order = 2)
```



#### Grouped Categorical


```{r summarytools Grouped Categorical}
summarytools::stby(
  list(x = mydata$LVI, y = mydata$LymphNodeMetastasis), 
  mydata$PNI,
  summarytools::ctable
  )
```



```{r summarytools Grouped Categorical 2}
with(mydata, 
     summarytools::stby(
       list(x = LVI, y = LymphNodeMetastasis), PNI,
       summarytools::ctable
       )
     )
```




```{r SmartEDA category 1}
SmartEDA::ExpCTable(
  mydata,
  Target = "Sex",
  margin = 1,
  clim = 10,
  nlim = NULL,
  round = 2,
  bin = 4,
  per = F
)
```





\pagebreak


---


### Continious Variables


```{r categorise cut off continious variables, eval=FALSE, include=FALSE}
questionr:::icut()
```



```{r select continious variables 1, eval=FALSE, include=FALSE}
mydataContinious <- mydata %>% 
    select(
        Yas,
        TumorCapi
    )
```



```{r define continious, eval=FALSE, include=FALSE}
mydataDescription <- describer::describe(iris)

mydataDescription %>% 
    janitor::clean_names() %>% 
    dplyr::filter(column_class == "numeric") %>% 
    dplyr::select(column_name) %>% 
    dplyr::pull() -> continiousVariables
```



```{r generate Code Continious, eval=FALSE, include=FALSE}
source(here::here("R", "gc_desc_cont.R"))
```



```{r generatedCodeContinious, child = here::here('childRmd', 'generatedCodeContinious.Rmd'), eval=FALSE, include=FALSE}
```



```{r tableone continious, eval=FALSE, include=FALSE}
tab <- tableone::CreateTableOne(data = pbc)
?print.ContTable
tab$ContTable
print(tab$ContTable, nonnormal = c("albumin", "copper"))
```



```{r explore continious variables, eval=FALSE, include=FALSE}
iris %>% explore::describe(Sepal.Length)
```


```{r SmartEDA, eval=FALSE, include=FALSE}
## Summary statistics by – overall
SmartEDA::ExpNumStat(
  Carseats,
  by = "A",
  gp = NULL,
  Qnt = seq(0, 1, 0.1),
  MesofShape = 2,
  Outlier = TRUE,
  round = 2
)
```





```{r inspectdf 3, eval=FALSE, include=FALSE}
inspectdf::inspect_num(storms, breaks = 10)

inspectdf::inspect_num(storms)$hist$pressure

inspectdf::inspect_num(storms, breaks = 10) %>%
  inspectdf::show_plot()

inspectdf::inspect_num(storms, storms[-c(1:10), -1])

inspectdf::inspect_num(storms, storms[-c(1:10), -1]) %>% 
  inspectdf::show_plot()
```














#### Split-Group Stats Continious


```{r summarytools Split-Group continious, eval=FALSE, include=FALSE}
grouped_descr <- stby(data = exams, 
                      INDICES = exams$gender, 
                      FUN = descr, stats = "common")
grouped_descr %>% tb()

grouped_descr %>% tb(order = 2)
```


```{r dlookr descriptives, eval=FALSE, include=FALSE}
carseats %>%
  group_by(US) %>% 
  dlookr::describe(Sales, Income) 

carseats %>%
  group_by(US, Urban) %>% 
  dlookr::describe(Sales, Income) 

```




```{r dlookr target, eval=FALSE, include=FALSE}
categ <- dlookr::target_by(carseats, US)
cat_num <- dlookr::relate(categ, Sales)
cat_num
summary(cat_num)
plot(cat_num)
```






#### Grouped Continious

```{r summarytools Grouped Continious, eval=FALSE, include=FALSE}
(iris_stats_by_species <- stby(data = iris, 
                               INDICES = iris$Species, 
                               FUN = descr, stats = c("mean", "sd", "min", "med", "max"), 
                               transpose = TRUE))
```



```{r summarytools Grouped Continious 2, eval=FALSE, include=FALSE}
with(tobacco, stby(BMI, age.gr, descr, 
                   stats = c("mean", "sd", "min", "med", "max"),
                   transpose = TRUE
                   )
     )
```



```{r summarytools Grouped Continious 3, eval=FALSE, include=FALSE}
tobacco$gender <- forcats::fct_explicit_na(tobacco$gender)
tobacco %>% group_by(gender) %>% descr(stats = "fivenum")
```



```{r SmartEDA category, eval=FALSE, include=FALSE}
## Summary statistics by – category
SmartEDA::ExpNumStat(
  Carseats,
  by = "GA",
  gp = "Urban",
  Qnt = seq(0, 1, 0.1),
  MesofShape = 2,
  Outlier = TRUE,
  round = 2
)
```



\pagebreak










